paper2_resistance_mechanisms_mixtures

### 2016-06-02 inst/documents/paper2_resistance_mechanisms_mixtures.Rmd
add & polish single insecticide scenarios

```{r,echo=FALSE,results='hide'}
  library(resistance)
```

### version 1

@@

*Before this add figures for effect of inputs on sole use.*

>>>>

```{r,echo=FALSE,results='hide'}
  library(resistance)
  library(ggplot2)
```

### version 2

@@

For single insecticide use, increasing the values of either effectiveness, exposure, dominance, or selective advantage, all lead to faster resistance (Figs a1-4). (In these four plots the value of the inputs not being varied are set at a constant 0.7 for effectiveness and 0.5 for the other 3).

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  a <- setExposure(exposure=0.5, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.9,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

  listOut <- runModel2( input )

  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=phi.SS1_A0)) + 
         labs(colour = "effectiveness") +
         coord_trans(y = "log10") +    
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a1. Effectiveness effect on single insecticide.")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  exposure <- 0.3
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  exposure <- 0.5
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  exposure <- 0.7
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

  listOut <- runModel2( input )

  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=exposure)) + 
         labs(colour = "exposure") +
         coord_trans(y = "log10") +    
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a2. Exposure effect on single insecticide.")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  #this sets exposures according to whether insecticide1, 2 or mixture
  a <- setExposure(exposure=0.5, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.3, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.7, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

  listOut <- runModel2( input )

  #plotallele.freq.andy(listOut, locus="1", sex="mf_mean", add_legend=FALSE)

  # now doing a better way
  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=h.RS1_A0)) + 
         labs(colour = "dominance") +
         coord_trans(y = "log10") + 
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a3. Dominance effect on single insecticide.")

```

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  a <- setExposure(exposure=0.5, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.3,
                      s.RR2_0B = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.7,
                      s.RR2_0B = 0.5 )

  #input <- cbind(input, inputOneScenario)
  input <- cbind(i1,i2,i3)

  listOut <- runModel2( input )

  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=s.RR1_A0)) + 
         labs(colour = "selective advantage") +
         coord_trans(y = "log10") +   
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a4. Selective advantage effect on single insecticide.")

```

When two insecticides are used the relative performance of a mixture strategy compared to sequential use is determined by the values of these four inputs.
